### 2015-07-14 text/ms.Rmd
Add reference to intro
Simplify paragraph

Population status and trajectory are two of the most fundamental values to
quantify in conservation biology [e.g. @mace2008; @iucn2015]. These properties
are key to everything from global assessments of extinction risk [e.g.
@stuart2004; @schipper2008] to assessing the sustainability of hunting and
fishing exploitation levels [e.g. @worm2009; @juan-jorda2011]. However,
conservation and ecological resource managers are often faced with reconciling
multiple uncertain and potentially conflicting estimates of status and
trajectory [e.g. @brodziak2010; @branch2011]. Some models may suggest a
population is at risk and declining in abundance while others may suggest it is
not at risk and stable.

@@

As @box1987 noted, all models are wrong, but they may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying the structure of the superensemble. For
example, when SSCOM estimates very low status this is likely the case,
conversely when COMSIR estimates low status, the truth is likely that the status
is high (Fig. \ref{partial-sim}). These models have two main differences: (1)
the form of effort dynamics and (2) the allowance for both measurement and
process error in SSCOM, whereas the implemented COMSIR admits measurement error
only. Were the methods to differ only in effort dynamics, the results point
towards a more suitable representation of effort dynamics at low biomasses in
SSCOM. We think that such investigation of the parameters of a superensemble may
lead to improvement in the mechanisms imparted to the individual models.

>>>>

Population status and trajectory are two of the most fundamental values to
quantify in conservation biology [e.g. @mace2008; @iucn2015]. These properties
are key to everything from global assessments of extinction risk [e.g.
@stuart2004; @schipper2008] to assessing the sustainability of hunting and
fishing exploitation levels [e.g. @worm2009; @juan-jorda2011]. However,
conservation and ecological resource managers are often faced with reconciling
multiple uncertain and potentially conflicting estimates of status and
trajectory [e.g. @brodziak2010; @branch2011; @deroba2015]. Some models may
suggest a population is at risk and declining in abundance while others may
suggest it is not at risk and stable.

@@

As @box1987 noted, all models are wrong, but they may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates very low status this is likely the case, conversely when COMSIR
estimates low status, the truth is likely that the status is high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the parameters of a superensemble may lead to
improvement in the mechanisms imparted to the individual models.
